\begin{thebibliography}{90}
\rhead[\fancyplain{}{\bfseries \leftmark}]{\fancyplain{}{\bfseries
\thepage}}

\addcontentsline{toc}{chapter}{\numberline{}{Bibliografia}}

\bibitem[BER 2006]{4} Berners-Lee, T. \emph{Linked data.} 2006, ultimo agg. June 18, 2009.\\
\url{http://www.w3.org/DesignIssues/LinkedData.html}

\bibitem[BER 2007]{3} Berners-Lee, T. \emph{Giant Global Graph}. In Decentralized Information Group, 21 November 2007.\\
\url{http://dig.csail.mit.edu/breadcrumbs/node/215}

\bibitem[CDG 2011]{13} Crofts, N., Doerr, M., Gill, T., Stead, S., Stiff, M. \emph{Definition of the CIDOC Conceptual Reference Model.} Version 5.0.4 (November 2011). ICOM/CIDOC CRM Special Interest Group.\\
\url{http://www.cidoc-crm.org/docs/cidoc_crm_version_5.0.4.pdf}

\bibitem[DKG 2011]{7} Damova, M., Kiryakov, A. Grinberg, M., Bergman, M., Giasson, F., Simov, K. \emph{Creation and Integration of Reference Ontologies for Efficient LOD Management.} In: Semi-Automatic Ontology Development: Processes and Resources, IGI Global, Hershey PA, USA, 2011.

\bibitem[DL190/1999]{16} DECRETO LEGISLATIVO 29 ottobre 1999, n. 490 - \emph{Testo unico delle disposizioni legislative in materia di beni culturali e ambientali}, a norma dell'articolo 1 della legge 8 ottobre 1997, n. 352.\\
\url{http://www.normattiva.it/uri-res/N2Ls?urn:nir:stato:decreto.legislativo:1999;490}

\bibitem[DOE 2010]{10} Doerr, M. (2010). \emph{The Europeana Data Model (EDM) mapping to CIDOC-CRM.}\\
\url{http://www.cidoc-crm.org/docs/CRM-EDM_FRBR.ppt}

\bibitem[DWG 2012]{9} De Boer V., Wielemaker J., Gent van J., Hildebrand M., Isaac A., Ossenbruggen van J., Schreiber G. (2012) \emph{Supporting Linked Data Production for Cultural Heritage Institutes: The Amsterdam Museum Case Study.} The Semantic Web: Research and Applications. LNCS Vol. 7295, pp 733-747.

\bibitem[ELL 2013]{5} Edelstein, L.G.a, Li-Madeo C., Marden J., Rhonemus A., Whysel N. (Spring 2013). \emph{Linked Open Data for Cultural Heritage: Evolution of an Information Technology.}\\
\url{http://www.whysel.com/papers/LIS670-Linked-Open-Data-for-Cultural-Heritage.pdf}

\bibitem[EDM]{11} EDM (Europeana Data Model). Documentation: \url{http://pro.europeana.eu/edm-documentation}

\bibitem[FGJ 1997]{26} Fernández-López, M., Gómez-Pérez, A. and Juristo, N. (1997). \emph{Methontology: From Ontological Art Towards Ontological Engineering.} In Proceedings of the 1997 AAAI Spring Symposium, SS-97-06: 33–40. Menlo Park, California, USA: AAAI Press. Retrieved from http://www.aaai.org/Papers/Symposia/Spring/1997/SS-97-06/SS97-06-005.pdf

\bibitem[FRBR]{19} FRBR (Functional Requirements for Bibliographic Records).\\
\url{http://www.ifla.org/publications/functional-requirements-for-bibliographic-records}

\bibitem[FRBR-CRM]{20} FRBR-CRM, FRBRoo.\\
\url{http://www.cidoc-crm.org/frbr_inro.html}

\bibitem[GMP 2014]{29} Gonano C.M., Mambelli F., Peroni S., Tomasi F. and Vitali F. (2014). \emph{Zeri e LODE. Extracting the Zeri photo archive to Linked Open Data: formalizing the conceptual model}. Bologna, 2014.

\bibitem[ICCDFot1999]{14} ICCD (Istituto Centrale per il Catalogo e la Documentazione), \emph{Beni fotografici.} 1999 (agg. 2004).\\
\url{http://www.iccd.beniculturali.it/index.php?it/387/beni-fotografici}

\bibitem[ICCDSto1999]{15} ICCD (Istituto Centrale per il Catalogo e la Documentazione), \emph{Beni storici e artistici.} 1992.\\
\url{http://www.iccd.beniculturali.it/index.php?it/253/beni-storici-e-artistici}

\bibitem[JCB 2011]{21} Jentzsch A. Cyganiak R., Bizer C. \emph{State of the LOD Cloud.} - (Version 0.3, 09/19/2011)\\
\url{http://lod-cloud.net/state/}

\bibitem[LSM 2013]{22} Lebo, T., Sahoo, S. and McGuinness, D. (2013). PROV-O: The PROV Ontology. W3C Recommendation, 30 April 2013. World Wide Web Consortium.\\
\url{http://www.w3.org/TR/prov-o/}

\bibitem[MLW 2013]{23} Marden J., Li-Madeo C., Whysel N., Edelstein J. (2013), \emph{Linked open data for cultural heritage: evolution of an information technology.} Proceeding SIGDOC '13, pp. 107-112. ACM New York, NY, USA.

\bibitem[MPP 2012]{24} Motik, B., Patel-Schneider, P. F. and Parsia, B. (2012). OWL 2 Web Ontology Language: Structural Specification and Functional-Style Syntax (Second Edition). W3C Recommendation, 11 December 2012. World Wide Web Consortium. Retrieved from http://www.w3.org/TR/owl2-syntax/

\bibitem[PCDHN]{25} Pan-Canadian Documentary Heritage Network (PCDHN) Linked Open Data (LOD) Visualization ``Proof-of-Concept''\\
\url{http://www.canadiana.ca/sites/pub.canadiana.ca/files/PC DHN\%20Proof-of-concept_Final-Report-ENG_0.pdf}

\bibitem[PES 2012]{6} Peroni, S. and Shotton, D. (2012). \emph{FaBiO and CiTO: Ontologies for describing bibliographic resources and citations.} Web Semantics: Science, Services and Agents on the World Wide Web, 17: 33–43. DOI: 10.1016/j.websem.2012.08.001

\bibitem[POL 2009]{1} Pollock, Jeffrey T. \emph{Semantic Web For Dummies}. Wiley, 2009. ISBN: 9780470396797.

\bibitem[PSV 2012]{18} Peroni, S., Shotton, D. and Vitali, F. (2012). \emph{Scholarly publishing and linked data: describing roles, statuses, temporal and contextual extents.} In H. Sack and T. Pellegrini (Eds.), Proceedings of i-Semantics 2012: 9– 16. New York, New York, US: ACM Press. DOI: 10.1145/2362499.2362502

\bibitem[PTV 2012]{8} Peroni S., Tomasi F. and Vitali F. (2012). \emph{Reflecting on the Europeana Data Model.} In: IRCDL 2012, pp. 228– 240. Communications in Computer and Information Science (CCIS) 354, Springer, Heidelberg, Germany 2012.

\bibitem[PTV 2013]{17} Peroni S., Tomasi F. and Vitali F. (2013). \emph{The aggregation of heterogeneous metadata in Web-based cultural heritage collections. A case study.} IJWET vol. 8, n. 4, pp. 412-432. ISSN 1476-1289. DOI: 10.154/IJWET.2013.059107

\bibitem[SMN 2013]{12} Scarselli T., Mancinelli M. L., Niccolucci F. (2013). \emph{Mapping ICCD Archaeological Data to CIDOC-CRM: the RA Schema.}\\
\url{http://www.academia.edu/5549957/Mapping_ICCD_arc haeological_data_to_CIDOC-CRM_the_RA_Schema}

\bibitem[USG 1996]{27} Uschold, M. and Gruninger, M. (1996). \emph{Ontologies: principles, methods and applications.} The Knowledge Engineering Review, 11(02): 93–136. DOI: 10.1017/S0269888900007797

\bibitem[VBG 2009]{28} Volz J., Bizer C., Gaedke M., and Kobilarov G. \emph{Discovering and maintaining links on the web of data.} In Proceedings of the 8th International Semantic Web Conference, pp. 650-665, 2009.

\bibitem[W3C2013]{2} W3C Data Activity \emph{W3C Semantic Web Activity Introduction}. Dec 2013.\\
\url{http://www.w3.org/2001/sw/}

\bibitem[ZEL 2006]{30} Zeldman J. emph{Web 3.0} In A List Apart, January 17, 2006.\\
\url{http://alistapart.com/article/web3point0}

\bibitem[SHA 2006]{31} Shannon V. \emph{A `more revolutionary' Web}, in The New York Times, May 23, 2006.\\
\url{http://www.nytimes.com/2006/05/23/technology/23iht-web.html?_r=0}

\end{thebibliography}